### 2021-01-25 biography.tex
Updates from Overleaf

\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/kiril_solovey.PNG}}
\noindent {\bf Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University, hosted by Prof. Marco Pavone. His research focuses on algorithmic aspects of robotics. He is particularly interested in the design and analysis of techniques for robot motion planning, multi-robot systems, and autonomous mobility-on-demand. He is supported by the Fulbright Scholars Program. Prior to Stanford, He was a Ph.D. student at Tel Aviv University working with Prof. Dan Halperin in the Computational Geometry Lab. He was supported by the Clore Israel Foundation.

>>>>

\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/kiril_solovey.PNG}}
\noindent {\bf Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University. He received his Ph.D. in Computer Science from Tel Aviv University, Israel. His work focuses on multi-robot systems and their applications to smart mobility, with an emphasis on the design of effective control and decision-making mechanisms. He is the recipient of the Clore Scholars Award, Fulbright Postdoctoral Fellowship, and several best paper awards and nominations.
